A Fast Unified Model for Parsing and Sentence Understanding

### 2016-06-13 writing/hard_stack_paper/paper.tex
Bib for paper submission; fix caption error.

\begin{table}[t]
\centering
\begin{tabular}{c @{\hspace*{1.5em}}c @{\hspace*{1.5em}} lc}
  \toprule
  $t$ & $S$[$t$] & \multicolumn{1}{c}{$Q_t$} & $a_t$ \\
  \midrule
  0 &   & \underline{\hphantom{0} \hphantom{0}} & \shift \\
  1 &  \word{Spot} & \hphantom{0} \underline{\hphantom{0} 1} & \shift \\
  2 &  \word{sat} & \hphantom{0} \hphantom{0} \underline{1 2} & \shift \\
  3  &   \word{down} & \hphantom{0} \hphantom{0} 1 \underline{2 3} & \reduce\\
  4  &   (\word{sat down}) & \hphantom{0} \hphantom{0} \underline{1 4} & \reduce\\
  5  & (\word{Spot} (\word{sat down})) & \hphantom{0} \underline{\hphantom{0} 5} &        \\
  \bottomrule
\end{tabular}
\caption{The thin-stack algorithm operating on the input sequence $\mathbf x = \text{(\word{Spot}, \word{sat}, \word{down})}$ and the transition sequence shown in the second column. $S$ is shown in the third column and represents the top of the stack at each step $t$. The last two elements of $Q$ (underlined) specify which rows $t$ would be involved in a \reduce\ operation at the next step.}
\label{tbl:thin-stack}
\end{table}

>>>>

\begin{table}[t]
\centering
\begin{tabular}{c @{\hspace*{1.5em}}c @{\hspace*{1.5em}} lc}
  \toprule
  $t$ & $S$[$t$] & \multicolumn{1}{c}{$Q_t$} & $a_t$ \\
  \midrule
  0 &   & \underline{\hphantom{0} \hphantom{0}} & \shift \\
  1 &  \word{Spot} & \hphantom{0} \underline{\hphantom{0} 1} & \shift \\
  2 &  \word{sat} & \hphantom{0} \hphantom{0} \underline{1 2} & \shift \\
  3  &   \word{down} & \hphantom{0} \hphantom{0} 1 \underline{2 3} & \reduce\\
  4  &   (\word{sat down}) & \hphantom{0} \hphantom{0} \underline{1 4} & \reduce\\
  5  & (\word{Spot} (\word{sat down})) & \hphantom{0} \underline{\hphantom{0} 5} &        \\
  \bottomrule
\end{tabular}
\caption{The thin-stack algorithm operating on the input sequence $\mathbf x = \text{(\word{Spot}, \word{sat}, \word{down})}$ and the transition sequence shown in the rightmost column. $S$[$t$] shows the top of the stack at each step $t$. The last two elements of $Q$ (underlined) specify which rows $t$ would be involved in a \reduce\ operation at the next step.}
\label{tbl:thin-stack}
\end{table}
